ggiraph text test

### 2021-02-17 _post/2021-02-17-ggiraphtext/ggiraphtext.Rmd
only theme_ipsum

```{r dev="svglite", eval=F}
gg_point = ggplot(data = data) +
  labs(title="long title long title long title")+
    geom_point_interactive(aes(x = wt, y = qsec, color = disp,
    tooltip = carname, data_id = carname)) +
  theme_ipsum_rc()+
  theme(plot.title=element_markdown())

>>>>

```{r dev="svglite", eval=T}
gg_point = ggplot(data = data) +
  labs(title="long title long title long title")+
    geom_point_interactive(aes(x = wt, y = qsec, color = disp,
    tooltip = carname, data_id = carname)) +
  theme_ipsum_rc()+
  theme(plot.title=element_markdown())
